Placeholder

### 2021-02-16 Paper_Histograms.Rmd
Added template code to plot sign up per month by study

>>>>

```{r Plot sign up per month by sample}

dat.retro_sign_up %>% 
  ggplot(aes(x = month, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  labs(x = "Month of sign up",
       y = "N participants") +
  theme(legend.position = "top",
        legend.title = element_blank(),
        axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25)
